Characterizing subarctic biomes for land surface modeling of pollution and climate risk

### 2021-03-02 VegOzone.tex
Start to revise Section 4.

\section{DO3SE modeling}
\label{sec:do3se}
To investigate which of the environmental factors lead to the observed ozone damage on clover and tobacco in 2018 in contrast to 2019, when no such damage was found on the clovers but only on the sensitive tobacco cultivar, we model the ozone uptake using the $\mathrm{DO_3SE}$ model and give an estimate on biomass reduction due to ozone uptake.

\subsection{Model description}
\label{subsec:model_describtion}

The opening of stomata is governed by different species-specific and environmental factors and can be described by a multiplicative model \citep{PTRS:Jarvis1976,ICP:MappingManual2017}:
\begin{equation}
  g^k_\text{sto} = g^k_\text{max} \cdot f^k_\text{phen} \cdot f^k_\text{light} \cdot \max{\left\{f^k_\text{min}, f^k_\mathrm{T} \cdot f^k_\mathrm{VPD} \cdot f^k_\text{SW}\right\}}.
  \label{eq:stomatal}
\end{equation}
%
Where $g_\mathrm{max}$ is the specific-specific maximum stomatal conductance value which is then modified by seasonal and environmental factors that vary within a range $0-1$. They are empirically determined and account for leaf phenology ($f_\text{phen}$), light ($f_\text{light}$), temperature ($f_\mathrm{T}$), water vapor pressure deficit ($f_\mathrm{VPD}$), and soil water content ($f_\text{SW}$). All factors differ with species or plant functional type (PFT) denoted with $k$.

@@

We hypothesize that perennial vegetation will likely prioritize their growth or fast adolescence throughout the short, sub-Boreal growing season and hence their carbon sequestration. Since the $\mathrm{DO_3SE}$ in its current state does not simulate $A_\mathrm{n}$, we assume for out purpose a first order proportionality between carbon uptake (photosynthesis) and $g_\mathrm{sto}$ and tune the species temperature and light response functions ($f_\mathrm{T}$ and $f_\mathrm{light}$) separately for higher stomatal conductance. For this purpose, we graphically intersected probability density functions (PDFs) of climatological data for temperature and global irradiance with the respective response function (Fig.~\ref{fig:f_temp_grassland} for grassland; for Norway spruce and birch see Appendix Figs.~\ref{fig:f_temp_spruce}--\ref{fig:f_temp_birch}). Formally, a parameterization is considered more optimal the larger the intersection area between the response function and PDF is.

>>>>

\section{DO3SE modeling}
\label{sec:do3se}
To investigate which of the environmental factors lead to the observed ozone damage on clover and tobacco in 2018 in contrast to 2019, when no such damage was found on the clovers but only on the sensitive tobacco cultivar, we model ozone uptake of different natural and semi-natural vegetation using the $\mathrm{DO_3SE}$ model and develop bespoke subarctic prameterizations for common plant species. In the following, we give an account of the $\mathrm{DO_3SE}$ model and the used method for deriving the bespoke parameters.

\subsection{Model description}
\label{subsec:model_describtion}
The opening of stomata is governed by different species-specific and environmental factors and can be described by a multiplicative model \citep{PTRS:Jarvis1976,ICP:MappingManual2017}:
\begin{equation}
  g^k_\text{sto} = g^k_\text{max} \cdot f^k_\text{phen} \cdot f^k_\text{light} \cdot \max{\left\{f^k_\text{min}, f^k_\mathrm{T} \cdot f^k_\mathrm{VPD} \cdot f^k_\text{SW}\right\}}.
  \label{eq:stomatal}
\end{equation}
%
Where $g_\mathrm{max}$ is the specific-specific maximum stomatal conductance value which is then modified by seasonal and environmental factors that vary within a range $0-1$. They are empirically determined and account for leaf phenology ($f_\text{phen}$), light ($f_\text{light}$), temperature ($f_\mathrm{T}$), water vapor pressure deficit ($f_\mathrm{VPD}$), and soil water content ($f_\text{SW}$). All factors differ with species or plant functional type (PFT) denoted with $k$.

@@

We hypothesize that perennial vegetation will likely prioritize their growth or fast adolescence throughout the short, subarctic growing season and hence their carbon sequestration. Since the $\mathrm{DO_3SE}$ in its current state does not simulate $A_\mathrm{n}$, we assume for our purpose a first order proportionality between $A_\mathrm{n}$ and $g_\mathrm{sto}$ \citep{GCB:Medlyn2011}. We then tune the species temperature and light response functions ($f_\mathrm{T}$ and $f_\mathrm{light}$) separately for higher stomatal conductance. We illustrate this procedure graphically by intersecting probability density functions (PDFs) of climatological data for temperature and global irradiance with the respective response function (Fig.~\ref{fig:f_temp_grassland} for grassland; for Norway spruce and birch see Appendix Figs.~\ref{fig:f_temp_spruce}--\ref{fig:f_temp_birch}). Formally, a parameterization is considered more optimal the larger the intersection area between the response function and PDF is.
